Development of User-Friendly\\System Identification Techniques

### 2016-08-17 front-and-back-matter/acknowledgements.inc.tex
Acknowledgments: almost finished

While the preparation of a PhD is for a large part an endeavor of a single person, it is by no means a solitary experience.
Research without collaboration is unthinkable and is unlikely to yield new scientific and technical insights since personal interactions allow new ideas and applications to germinate.

In the first place, I would like to thank my colleagues at the ELEC department for being an outgoing group that has been combining a fond interest for engineering, science, and leisure.
In particular, I am grateful for the great atmosphere in the office and for my office mates over the last few years: Adam, Anna, David, Diane, Ebrahim, Erlyiang, Francesco, Gustavo, Hannes, Maarten, Mark, Matthias, and Maulik (though not all at the same time).
I have fond memories of the time Alexandra and I spend together with Anna and Maarten on our road trip in South Africa and watching the local wildlife.
I have also enjoyed the no-frills company of Adam, his overall good taste as an engineer and dry sense of humor (`nobody expects the Cauchy distribution' was a sparkle of laughter after barren days).
On the diametrical opposite side of the spectrum, but not less agreeable, were my interactions with Matthias.
I really appreciate his deep knowledge and his frankness, which often came into play when the both of us were having rougher times.

@@

@@

%FIXME mikaya, John
%FIXME istvan

%FIXME Johan
%FIXME Tom

%FIXME Matthijs
%FIXME CST
%FIXME Rick, Annemiek, Frank,  MST

I would also like to express my sincere gratitude for my jury member for their flexibility and great effort in aiding me to ameliorate this dissertation and my understanding of connections of my work to other fields of science and engineering.
In retrospect, I have absolutely enjoyed discussing with them during my private defense and the few hours afterwards.
In particular, I have been astounded by the huge amount of work that Koen put into being the best secretary that I would not even have dared dreaming of.
Also, I appreciate Tomas for taking the time to go through the draft version of this dissertation with me in painstaking detail in the hours after my private defense.

This book also would not have been possible without my fellow members of the matlab2tikz team: Nico, Oleg, Peter, Michael and a handful of incidental other helpers.
Most of the graphs in this text have, at one point or another, passed through the matlab2tikz codebase.
I have been really enjoying our collaboration, getting-things-done attitude, and discussions regarding good coding practices in \MATLAB{} and the future directions of the matlab2tikz project.

>>>>

While a PhD only has a single author, it is by no means a solitary experience.
Research without collaboration is unlikely to yield new scientific and technical insights since personal interactions allow new ideas and applications to germinate.
Hence, I am very grateful for the scientific interactions that have improved and deepened this work.

In the first place, I would like to thank my colleagues at the ELEC department for being an outgoing group that has been combining a fond interest for engineering, science, and leisure.
In particular, I am grateful for the great atmosphere in the office and for my office mates over the last few years: Adam, Anna, David, Diane, Ebrahim, Erlyiang, Francesco, Gustavo, Hannes, Maarten, Mark, Matthias, and Maulik (though not all at the same time).
I have fond memories of the time Alexandra and I spend together with Anna and Maarten on our road trip in South Africa and going on a safari to see the local wildlife and smell the wild lavender.
I have also enjoyed the no-frills company of \textsc{Adam}, his overall good taste as an engineer and dry sense of humor (`nobody expects the Cauchy distribution' was a sparkle of laughter after barren days).
On the diametrical opposite side of the spectrum, but not less agreeable, were my interactions with Matthias.
I really appreciate his deep knowledge and his frankness, especially when the both of us were having rougher times.

@@

During the few summers that I spent at ELEC, I have been fortunate enough to have collaborated with Mikaya and John, on what has become a considerable part of this dissertation.
I really admire Mikaya's \latin{joie de vivre}, which really made his visits to Brussels a time to look forward to each year.
Most of the work happened under supervision from John, who is an excellent researcher and, I think, what a future professor should look like: scientifically correct, but with a humane management style.

@@

During my first real international conference, I was happy to meet with István Kollár, who has unfortunately passed away recently. 
I have really enjoyed our scientific discussions, grabbing some beers, and the view he offered into the foregone era of the Iron Curtain.

%FIXME Johan

In the second year of my PhD, I have been a visiting researcher in the Control Systems Theory group of prof. Maarten Steinbuch.
I remember my first encounter with Maarten as a friendly, but rather critical, meeting which took me aback for a few minutes.
I have great admiration for Maarten's very enjoyable mix of scientific accuracy, critical business acumen and lightheartedness.
During these months at the CST group, I much enjoyed the company of Matthijs, Frank, Annemiek and Rick.
I was very happy to have had the chance to interact with Rick who had an excellent understanding of the set-up that I was working on and who was always available to discuss or joke around.
Also, I took great pleasure in interacting with Matthijs: during his time at ELEC, my time at CST, and all of the times we hung out as colleagues or as friends.
Overall, I would like to thank all the people (PhD students, professors, secretaries, ...) at CST for their open and warm atmosphere.

However, my main scientific interactions in Eindhoven have been with Tom, who eventually became my promotor.
I have always enjoyed our discussions and the broad and deep scientific knowledge he masters and yet is able to explain with clarity.
Thanks to his very open attitude, I was able to learn a whole lot in quite a short time.

I would also like to express my sincere gratitude for my jury member for their flexibility and great effort in aiding me to ameliorate this dissertation and my understanding of connections of my work to other fields of science and engineering.
In retrospect, I have absolutely enjoyed discussing with them during my private defense and the few hours afterwards.
In particular, I have been astounded by the huge amount of work that Koen put into being a great secretary.
Also, I appreciate Tomas for taking the time to go through the draft version of this dissertation with me in painstaking detail in the hours after my private defense.

This book also would not have been possible without my fellow members of the matlab2tikz team: Nico, Oleg, Peter, Michael and a handful of incidental other helpers.
Most of the graphs in this booklet have passed through the matlab2tikz codebase.
I have been really enjoying our collaboration, getting-things-done attitude, and discussions regarding good practices for making figures and coding in \MATLAB{}, and the future directions of the project.
